---
title: "Class 11 : Structural Bioinformatics 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##The PDB Database

PDB Database Composition
We've set column 1 as the row names for this data set
```{r}
stats <- read.csv("Data Export Summary.csv", row.names = 1)
stats
```

Q1: Determine the percentage of structures solved by X-Ray and Electron Microscopy. Also can you determine what proportion of structures are protein

```{r}
sum(stats$Total)
sum
```

Above code solves for total data in all entire stats data set 
Let's separate these by methods
```{r}
pre.by.method <- stats$Total/sum(stats$Total)*100
names(pre.by.method) <- rownames(stats)
pre.by.method
```

Q: What proportion of structures are protein? 
```{r}
byprotein <- sum(stats$Proteins)/sum(stats$Total)*100
round(byprotein, 2)
```
To install R Data pasta:  install.packages("datapasta") in console
```{r}
data.frame(stringsAsFactors = FALSE,
   Experimental.Method = c("X-Ray", "NMR", "Electron Microscopy", "Other",
                           "Multi Method", "Total"),
              Proteins = c(124770, 10988, 2057, 250, 127, 138192),
         Nucleic.Acids = c(1993, 1273, 31, 4, 5, 3306),
    ProteinNA.Complex = c(6451, 257, 723, 6, 2, 7439),
                 Other = c(10, 8, 0, 13, 1, 32),
                 Total = c(133224, 12526, 2811, 273, 135, 148969)
)

```

## Introduction to Bio3D in R
 
Load the Bio3D package; list fns via lbio3d() in consol 
```{r}
library(bio3d)

```

```{r}
hsg1 <- read.pdb("1hsg.pdb")
hsg1
```

```{r}
pdb <- read.pdb("1hsg")
```

So Barry's lab has this dev version of bio3d that allows for 3D biomolecular structure viewing in R itself. Then you don't have to rely on opening written-out PDB files in programs such as VMD or PyMol

```{r}
#install.packages("devtools")
#devtools::install_bitbucket("Grantlab/bio3d-view")

```

Let's try it out
```{r}
library(bio3d.view)
library(rgl)
```
```{r}
view(pdb)
```
Nope, can't load the rgl package. 

Moving on with our lives-- 

Extract the protein only portion of this PDB structure: 
#Section 4: Atom Selection
```{r}
ca.inds <- atom.select(pdb, "calpha")
ca.inds
```

Atom indices is the atom # I think.. And the xyz is the numeric vector to access the xyz componnet of the input PDB structure object 

So there are 198 calpha's in pdb.. , each with its 3# xyz coordinate (198 x 3 = 594)

But where exactly are they?

```{r}
pdb$atom[ca.inds$atom,]
```
Here, these results indicate that the Calpha's are located @ location 2, 9, 18, 26,... etc . A quick way to check this is to do str(ca.inds) in the R console 


```{r}
head(pdb$atom[ca.inds$atom,])
```

Let's try to extract the ligand & write out to a separate file? 
```{r}
inds <- atom.select(pdb,"ligand")
inds
```

There are 45 ligands! :D 
Let's find out where they are! 
```{r}
pdb$atom[inds$atom,]

```

What's going on lmao 

```{r}
ligand.pdb <- trim.pdb(pdb, inds)
ligand.pdb
```
Uhhhh, think we trimmed out the ligand(we named inds) from the PDB file. 
```{r}
library(bio3d.view)
library(rgl)
view(ligand.pdb)
```
View still not working. 

```{r}
write.pdb(ligand.pdb, file = "ligand.pdb")
```

For fun 
```{r}
pdb <- read.pdb("1HEL")
# Normal mode Analysis
modes <- nma(pdb)
plot(modes)
```
```{r}
m7 <- mktrj(modes, mode = 7, file = "mode_")
```

