---
title: "Class 09"
author: "Kathreeni"
date: "2/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read our input data

```{r}
#Save input data file to a new 'data' directory
fna.data <- "WisconsinCancer.csv"
wisc.df <- read.csv(fna.data)
```

Always double check the data.. 
```{r}
#Head checks the first 6 items in each column 
head(wisc.df)
```
Looks like there is a funny last column "x", let's check how many samples (i.e patients, rows) and features (i.e. columns) are in this data set
```{r}
#number of patients : important to keep in mind that row 1 is the feature titles
nrow(wisc.df[])

#number of features : imp to keep in mind that column 1 is just patient id, col 2 is ID, so we only want 3 and onwards; AND we want to get rid of the last funny colum 
ncol(wisc.df[3:32])
wisc.data <- wisc.df[, 3:32]
head(wisc.data)
```
Add patient ID as row names of our data 

```{r}
rownames(wisc.data) <- wisc.df$id
#use head again just to make sure we put it in correctly 
head(wisc.data)
```
If we just want to call out specific columns, we call them out individually using c()

```{r}
wisc.df[, c(4,10,21)]
```

Q: How many cancerous samples (Benign vs Malignant) are there? 

```{r}
table(wisc.df$diagnosis)
```

Q: How many features are "_mean" values? 

```{r}
#grep searches for matches by argument pattern within each element of a character vector
#grep(pattern, x) : will output a vector indicating integers inside the total columns that match with your pattern
#Adding length() will count the number of values output by grep

length(grep("_mean", colnames(wisc.data)))
```

```{r}
inds <- grep("_mean", colnames(wisc.data))
colnames(wisc.data)[inds]

```


Principal Component Analysis (PCA)

Important to first check if data needs to be scaled before performing PCA bc 1) Input variables use different units of measurements and 2) Input variables have slightly different variances 

Determine if it has to be scaled by checking the mean and standard deviaton 
```{r}

colMeans(wisc.data)
# apply() will take the input data, function you want to apply, and apply it to the selections you specify apply(input, 1(for rows) or 2(for columns), function)
apply(wisc.data, 2,mean)
```

To round the data.. 
```{r}
#round to 3 decimal places
round(apply(wisc.data, 2, mean),3)
```

Execute PCA with prcomp() function, and save it to wisc.pr

```{r}
wisc.pr <- prcomp(wisc.data, scale = TRUE)
summary(wisc.pr)
```
Eg PC1 means that 44.27%..
PC2 indicates that it doesnt do as well as PC1, accounts for 18.97%. 
Cumulative Proportion is PC1 cumulative + PC2's 18.97%, 

```{r}
biplot(wisc.pr, choices = 1:2)
#Here it makes a plot using the rownames as plotting character for biplots, choices 1:2 is referring to PC1 and PC2 of wisc.pr
```

TO make this cleaner to see, we can make a more standard scatter plot of each observation along PC1 and PC2 ; if you read wisc.pr, you'll see that wisc.pr$x specifies a matrix with the PC's and columns. 
```{r}

plot(wisc.pr$x[,1], wisc.pr$x[,2], xlab = "PC1", ylab = "PC2")
```


To color the plot.. 
What do we want to color? 
```{r}
#Let's color via diagnosistic result via wisc.df$diagnosis
plot(wisc.pr$x[,1], wisc.pr$x[,2], col = wisc.df$diagnosis, xlab = ("PC1"), ylab = ("PC2"))
```

##Make a screen-plot for our PCA results
This plot will show the proportion of variance captured in each PC 

```{r}
#wisc.pr (sdevation ) squared will yield the variance
variance <- wisc.pr$sdev^2
#want itin proportion
variance/sum(variance)
#Make it into a percentage
pve <- round(variance/sum(variance)*100, 2)
```

NOw let's plot it! 
```{r}
plot(pve, xlab = "Principal Component", ylab = "Proportion of Variance Explained", type = "o")
```

But let's plot it using a data-driven y-axis 
```{r}

barplot(pve, xlab = "Principal Component", ylab = "Proportion of Variance Explained", axes = FALSE, names.arg = paste("PC", 1:length(pve)))
axis(2, round(pve))
```

```{r}
#dist to calculate distance between the data points in PC1 and 2
d <- dist(wisc.pr$x[,1:2])
#hierarchial clustering is hclust
hclust(d, method = "ward.D2")
#ward.D2 is a method of hclust
```

```{r}

d <- dist(wisc.pr$x[,1:2])
#let's see wtf this d is
d
```

Uh okay. WHat's the hclust??
```{r}
hc <- hclust(d, method = "ward.D2")
hc
```
```{r}

d <- dist(wisc.pr$x[,1:2])
hc <- hclust(d, method = "ward.D2")
plot(hc )
```
Anddddd we're cutting trees... in 3 mini.. trees(ie clusters)

```{r}
cutree(hc, k = 3)
#k = 3 groups that we're cutting into???? so this gives us all the patient id's with the group they're cut into (groups 1  / 2/ or 3)
grp3 <- cutree(hc, k = 3)
```


How do we know how many patients are in each group? Use the table function derpy derp 

```{r}
table(grp3)
```

Let's plot the PCA plot colored by the cluster these patients belong in 

```{r}
plot(wisc.pr$x[,1], wisc.pr$x[,2], xlab = "PC1", ylab = "PC2", col = grp3)
```
See how the graph now shows that there's 3 clusters in our originally 2-dimentioned graph of PC1 and PC2? 

Welp!!!??!?!?!?!?!??!!

Cross Tabulaton! 

```{r}
#table(grp,)
#We're making 0 for benign and 1 for malignant, quantifying B vs M 
diagnosis <- wisc.df$diagnosis == "M"
#basically making additional tables within the grp3 set up 
table(grp3, diagnosis)

```

Easier version of the stuff above 
```{r}
table(grp3, wisc.df$diagnosis )
```

If you set k = higher number at the cuttree, and table it again, it further analyzes the clusters within bigger clusters; eg within people who are blue, who are active/inactive

```{r}
#url <- "new_samples.csv"
url <- "https://tinyurl.com/new-samples-CSV"
new <- read.csv(url)
npc <- predict(wisc.pr, newdata = new)
npc

```

What's going on ; so.. they're 2 patients and their ranking on these diff PC's? 
```{r}
plot(wisc.pr$x[,1:2], col= wisc.df$diagnosis)
points(npc[,1], npc[,2], col=c("green", "blue"), cex = 2)
```
Based on their locations, which patient is more imortant to follow up with? 
