---
title: "Class 12: Structural Bioinformatics Drug Discovery"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Clean up our proten target structure

First we download a target (i.e protein receptor) structure from the main PDB database. We will pick PDB ID "1hsg"

To use the bio3d package, we must library() it again. This code makes it so that in the future all you have to do is to change the argument to pdb.code and the entire script will run again but for the newly specified protein. 
```{r}
library(bio3d)
pdb.code <- "1hsg"
file.name <- get.pdb(pdb.code)
```

Extract the protein only segment of this PDB entry and write out a new PDB format fle. We will also do the same for the bound ligand. 

```{r}
hiv <- read.pdb(file.name)
hiv
```
use "file.name" here because it is not hardcoded. If you used "1HSG.pdb" then this s a ine that you'd have to change again and again each time you run ths script. 

After reading hiv above, whoa too much data. We just want the protein segment!
```{r}
prot <- trim.pdb(hiv, "protein")
prot
```
```{r}
prot.filename <- paste(pdb.code, "_protein.pdb", sep="")
write.pdb(prot, file=prot.filename)
```

Now try this for the ligand :o 
```{r}
lig <- trim.pdb(hiv,"ligand")
lig
```
```{r}
lig.filename <- paste(pdb.code, "_lig.pdb", sep="")
write.pdb(lig, file=lig.filename)
```

In terminal: mv ~/1hsg_protein.pdbqt . moves the file 1hsg.pdbqt from home (~/) to current location (.)

 ~/Downloads/autodock_vina_1_1_2_mac/bin/vina --config config.txt --log log.txt
##Convert our docking results for viewing in VMD
```{r}
res <- read.pdb("all.pdbqt", multi = TRUE)
res
```
```{r}
write.pdb(res, file = "results.pdb")
```

```{r}
res <- read.pdb("all.pdbqt", multi = TRUE) 
ori <- read.pdb("ligand.pdbqt")
rmsd(ori, res)
```

