---
title: "Class 6 R Functions"
author: "Kathreeni"
date: "1/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## File reading (again!)

Here we try to use **read.table()** and friends to input some example data into R 

Let's insert a code chunk, by pressing the "insert" button 
```{r}
read.table("https://bioboot.github.io/bggn213_S18/class-material/test1.txt", header = TRUE, sep = ",")
```
```{r}
file1 <- "https://bioboot.github.io/bggn213_S18/class-material/test1.txt"
read.csv(file1)
```
```{r}
read.table("https://bioboot.github.io/bggn213_S18/class-material/test2.txt", sep = "$", header = TRUE)
```
```{r}
file2 <- "https://bioboot.github.io/bggn213_S18/class-material/test2.txt"
read.table(file2, sep = "$", header = TRUE)
```
```{r}
read.table("https://bioboot.github.io/bggn213_S18/class-material/test3.txt")
```
```{r}
file3 <- "https://bioboot.github.io/bggn213_S18/class-material/test3.txt"
read.table(file3)
```
## R functions

My first function 

```{r}
add <- function(x, y=1) {
# Sum the input x and y 
  x + y
}
```
Let's use the **add()** function 

```{r}
add(1)
```
```{r}
add(1, 5)
```

```{r}
add(1, 4)
add(c(1,2,3))
```
```{r}
#add(1,2,3)
```


```{r}
rescale <- function(x){
  rng <- range(x)
  (x - rng[1])/(rng[2] - rng[1])
}
```

```{r}
rescale(1:5)
```
```{r}
rescale2 <- function(x){
  rng <- range(x, na.rm = TRUE)
  (x - rng[1])/(rng[2]-rng[1])
}
```

```{r}
rescale2(c(2,3,NA,4,NA,1))
```


```{r}
rescale3 <- function(x, na.rm=TRUE, llama=TRUE) {
   if (na.rm) {
     rng <- range(x, na.rm = na.rm)
   } else {
     rng <- range(x)
   }
      print("Hello")
      answer <- (x - rng[1]) / (rng[2] - rng[1])
      return(answer)
   print("is it me you are looking for?")
   if (llama) {
      plot(answer, typ ="b",lwd = 4)
     print("please stop")
}
   print("I can see it in ...")
}
```
##return auto finishes fxn and moves to next thing , can be children'd 

##Using the bio3d package
```{r}
library(bio3d)
```
```{r}
pdb <- read.pdb("1hbs")
```

What is in this **pdb** thing? 
```{r}
pdb
```

elety	a character vector of atom names.
chain	a character vector of chain identifiers.
```{r}
#Can you improve this analysis code?
library(bio3d)
s1 <- read.pdb("4AKE")  # kinase with drug
s2 <- read.pdb("1AKE")  # kinase no drug
s3 <- read.pdb("1E4Y")  # kinase with drug
s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s3, chain="A", elety="CA")
s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b
plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```
```{r}
#Can you improve this analysis code?
library(bio3d)
s1 <- read.pdb("4AKE")  # kinase with drug
s2 <- read.pdb("1AKE")  # kinase no drug
s3 <- read.pdb("1E4Y")  # kinase with drug
trim_plot <- function(x){
    x.chainA <- trim.pdb(x, chain = "A", elety = "CA")
    x.b = x.chainA$atom$b
    plot(x.b, sse = x.chainA, typ = "l", ylab = "Bfactor")
}
trim_plot(s1)
trim_plot(s2)
trim_plot(s3)